Percussive Sound Generation with Virtual Listeners and Modular Synthesizers

### 2020-08-21 templates_aimusic2020/paper.tex
Updates from Overleaf

 \begin{figure}[t]
    \begin{center}
    \textbf{Generative System}
    \makebox[\textwidth]{
    \fbox{\includegraphics[width=1\linewidth]{images/pipeline.pdf}}}
    \end{center}
    \caption{A blueprint of our system which allows each component to be implemented in a number of ways. Our implementations of this pipeline allow for easy parallelization when needed. This implementation also allows for easy integration of heuristic search for future works. 
    }
\label{fig:pipeline_outline}
\end{figure}

@@

\section{Virtual Synthesizer Design}
\begin{table}[htbp]
\centering
\resizebox{\columnwidth}{!}{\begin{tabular}{ |p{4cm}|p{4cm}|p{4cm}| } 
\hline
Parameters & Value Range & notes and constraints\\
\hline \hline
Attack & 0-3 & A-D-S-R values relative\\
Decay & 0-3 & relative to A-S-R\\
Sustain & 0-3 & relative to A-D-R\\
Release & 0-3 & relative to A-D-S\\
OSC type & sine,square,saw & -\\
IsNoise & boolean & generate noise using \newline cloud of waveform\\
Length & 0-1 second & - \\
StartTime & 0-1 second & Length+Start$<$1\\
Amplitude & 0.1-1 & 1 = max amplitude\\
Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
HP filter Cuttoff & 0-20000hz & -\\
LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
Filter Order & 4,8,16 & butterworth filter order \\
\hline
\end{tabular}}
\caption{Synthesizer submodule Parameters. Despite the simplicity of the parameters and our efforts at constraining the ranges, the number of parameters that can be randomly chosen for each submodule is over $10^{15}$. Each synthesizer can contain any number of submodules }
\label{table:submodule_params}
\end{table}
Digital sound is a series of discrete values. \textit{Digital synthesis} of audio is the process of creating these values. Here, we do not employ probabilistic models for the synthesizer component. Our decision is based on the following factors:
\begin{itemize}
    \item \textit{Novelty and Creativity}: Given large sets of examples, generative models such as VAEs and GANS have proven capable of generating samples similar to the exemplars. In this work, we are not aiming for perfect imitations. We seek to create \emph{novel sounds} by via artificial, exploratory creativity. Boden defines this concept as an emergent property of generative work within confined rule sets~\cite{boden2009computer}. Ultimately, we wish to work within the limitations of any tractable sound source to create its approximations of a given sound category. Within the music realm, a prominent instance of exploratory creativity is the persistent aesthetics of 8-bit soundtracks, remaining popular long after the original constraints are lifted~\cite{collins2007loop}.
    \item \textit{Interpretability}: Neural networks are often described as black boxes~\cite{basheer2000artificial}. Their highly recursive structure makes modern explanation methods such as saliency maps unreliable~\cite{rudin2019stop}.  
    \item \textit{Speed of Rendering at high sampling rates}: Despite the utilization of powerful GPUs, the standard sampling rate in most audio generation work utilizing neural networks is under 24 khz ~\cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}. However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}. At our fixed sampling rate of 48 khz, synthesizers with stack sizes of 8 can create and save 1 sounds to hard-disk with an average rendering time of 50 milliseconds\footnote{Using a single process on a Macbook Air 2012 and Ubuntu 18.04}. 
    \item \textit{Flexibility and Scaling}: Probabilistic audio generation is often done sequentially. For example, state of the art, parallel wave generation with GANs requires a fixed amount for rendering time for each time-step~\cite{yamamoto2020parallel}. Our virtual synthesizer produces audio by solving a linear system of equations. The added footprint of increasing the length of rendered sounds or higher sampling rates is relatively minuscule.  
\end{itemize}

@@

@@

\section{Virtual Ear}

We are not looking for the perfect imitation of organic drums using a synthesizer. We seek to imitate drums using a synthesizer and even \textbf{prefer} for its generations to retain novel, unusual characteristics. The task assigned to the virtual ear is the rare acceptance of drum-like sounds and the inevitable rejection of most \enquote{noise} outputs from the virtual synthesizer. The virtual ear makes two critical decisions: 
\emph{
\begin{quote}
\text{Decision.1 Could the sound be used as a drum?}\label{Decision.1}
\\
\text{Decision.2 If it does sound like a drum, what type of drum should it be?}\label{Decision.2}
\end{quote}
 }

>>>>

 \begin{figure}[t]
    \begin{center}
    % \textbf{Generative System}
    \makebox[\textwidth]{
    \fbox{\includegraphics[width=1\linewidth]{images/pipeline.pdf}}}
    \end{center}
    \caption{A blueprint of our system which allows each component to be implemented in a number of ways. Our implementations of this pipeline allow for easy parallelization when needed. This implementation also allows for easy integration of heuristic search for future works. 
    }
\label{fig:pipeline_outline}
\end{figure}

@@

\section{Virtual Synthesizer Design}
\begin{table}[htbp]
\centering
\resizebox{\columnwidth}{!}{\begin{tabular}{ |p{4cm}|p{4cm}|p{4cm}| } 
\hline
Parameters & Value Range & notes and constraints\\
\hline \hline
Attack & 0-3 & A-D-S-R values relative\\
Decay & 0-3 & relative to A-S-R\\
Sustain & 0-3 & relative to A-D-R\\
Release & 0-3 & relative to A-D-S\\
OSC type & sine,square,saw & -\\
IsNoise & boolean & generate noise using \newline cloud of waveform\\
Length & 0-1 second & - \\
StartTime & 0-1 second & Length+Start$<$1\\
Amplitude & 0.1-1 & 1 = max amplitude\\
Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
HP filter Cuttoff & 0-20000hz & -\\
LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
Filter Order & 4,8,16 & butterworth filter order \\
\hline
\end{tabular}}
\caption{Synthesizer submodule parameters. Despite the simplicity of the parameters and our efforts at constraining the ranges, the number of parameters that can be randomly chosen for each submodule is over $10^{15}$. Each synthesizer can contain any number of submodules}
\label{table:submodule_params}
\end{table}
Digital sound is a series of discrete values. \textit{Digital synthesis} of audio is the process of creating these values. Here, we do not employ probabilistic models for the synthesizer component. Our decision is based on the following factors:
\begin{itemize}
    \item \textit{Novelty and Creativity}: Given large sets of examples, generative models such as VAEs and GANS have proven capable of generating samples similar to the exemplars. In this work, we are not aiming for perfect imitations. We seek to create \emph{novel sounds} by via artificial, exploratory creativity. Boden defines this concept as an emergent property of generative work within confined rule sets~\cite{boden2009computer}. Ultimately, we wish to work within the limitations of any tractable sound source to create its approximations of a given sound category. Within the music realm, a prominent instance of exploratory creativity is the persistent aesthetics of 8-bit soundtracks, remaining popular long after the original constraints are lifted~\cite{collins2007loop}.
    \item \textit{Interpretability}: Neural networks are often described as black boxes~\cite{basheer2000artificial}. Their highly recursive structure makes modern explanation methods such as saliency maps unreliable~\cite{rudin2019stop}.  
    \item \textit{Speed of Rendering at high sampling rates}: Despite the utilization of powerful GPUs, the standard sampling rate in most audio generation work utilizing neural networks is under 24 khz ~\cite{yamamoto2020parallel,oord2017parallel,aouameur2019neural,ramires2020neural}. However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}. At our fixed sampling rate of 48 khz, synthesizers with stack sizes of 8 can create and save 1 sounds to hard-disk with an average rendering time of 50 milliseconds\footnote{Using a single process on a Macbook Air 2012 and Ubuntu 18.04}. 
    \item \textit{Flexibility and Scaling}: Probabilistic audio generation is often done sequentially. For example, state of the art, parallel wave generation with GANs requires a fixed amount for rendering time for each time-step~\cite{yamamoto2020parallel}. Our virtual synthesizer produces audio by solving a linear system of equations. The added footprint of increasing the length of rendered sounds or higher sampling rates is relatively minuscule.  
\end{itemize}

@@

 \begin{figure}[t]
    \begin{center}
    % \textbf{Synthesizer SubModule }
    \makebox[\textwidth]{
    \fbox{\includegraphics[width=1\linewidth]{templates_aimusic2020/images/synthesizer_block.pdf}}}
    \end{center}
    \caption{High level representation of pre-rendering steps for each submodule. Each Synthesizer contains 1 or more these submodules. The output of a synthesizer is the normalized addition of all its submodule outputs. Each synthesizer program determines the number of these submodules and their parameters. 
    }
\label{fig:pipeline_outline}
\end{figure}

@@

\section{Virtual Ear}
The task assigned to the virtual ear is the rare acceptance of drum-like sounds and the inevitable rejection of most \enquote{noise} outputs from the virtual synthesizer. Our goal is not realism; We want the virtual ear to accept novel and unusual drum sounds. The virtual ear makes two critical decisions: 
\emph{
\begin{quote}
\text{Decision.1 Could the sound be used as a drum?}\label{Decision.1}
\\
\text{Decision.2 If it does sound like a drum, what type of drum should it be?}\label{Decision.2}
\end{quote}
 }
